### 2010-03-29 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: don't present Fin as a tagged constructor, but mention the possibility.

\[\stk{
\VecD : \Set \To \TagIDesc{\Nat} \\
\begin{array}{@{}ll}
\VecD\: \V{X} = \\ \quad\bigRedBracket{ 
            \begin{array}{l}
                \pair{[]}{\_}{} 
                \\\\
                \bigRedBracket{
                \begin{array}{l} 
                  \LAM{\V{n}} \caseB{\V{n}}{\NatZero \mapsto [\VecNil] \\
                                   (\NatSuc \V{n}) \mapsto [\VecCons{}{}]} \\
                  \LAM{\V{n}} \caseB{\V{n}}{\NatZero \mapsto [\DConst{\Unit}] \\
                                   (\NatSuc \V{n}) \mapsto [\DSigma{\V{X}}{\DVar{\V{n}}}]}
                \end{array}}
            \end{array}}
\end{array}
}\]

@@

Equations have simply disappeared. We should precise that forcing a
description is not guaranteed to remove all constraints. It is subject
to future work to see if constraints can be entirely eradicated, or
presented more conveniently to the user. Finally, it is worth
mentioning that the forcing optimisation is a \emph{source-to-source}
transformation of the description.

>>>>

\[\stk{
\VecD : \Set \To \TagIDesc{\Nat} \\
\begin{array}{@{}ll}
\VecD\: \V{X} = \\ \quad\bigRedBracket{ 
            \begin{array}{l}
                \pair{[]}{\_}{} 
                \\\\
                \bigRedBracket{
                \begin{array}{l} 
                  \LAM{n} \caseB{n}{\NatZero \To [\VecNil] \\
                                   (\NatSuc n) \To [\VecCons{}{}]} \\
                  \LAM{n} \caseB{n}{\NatZero \To [\DConst{Unit}] \\
                                   (\NatSuc n) \To [\DSigma{X}{\DVar{n}}]}
                \end{array}}
            \end{array}}
\end{array}
}\]

@@

Equations have simply disappeared. Note that it is straightforward to
turn this definition into a tagged form. We should precise that
forcing a description is not guaranteed to remove all constraints. It
is subject to future work to see if constraints can be entirely
eradicated, or presented more conveniently to the user. Finally, it is
worth mentioning that the forcing optimisation is a
\emph{source-to-source} transformation of the description.
